Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-04 manuscript-chicago.Rmd
More edits to discussion

Finally, the coupling between negative-only event counts and social cohesion
also remained relatively similar but demonstrated some important differences.
First, we see a greater number of windows at above-chance levels for RR,
including an interesting spike around window 32 that suggests a negative
externally focused action taken by Syria prompted a sharp rise in social
cohesion. (This would not have been captured by the target-only dataset.)
Second---like with the all-event data---we see different structuring of the data
through differences in the patterns of DET; above-chance DET only occurrs within
the middle of the observation period, around a time of increased strive (as
noted above).

@@

Nonlinear methods have been transformative for a variety of research areas
[including psychology, @coco2014cross]. One of the goals in the present work was
to introduce variants of one kind of nonlinear method---specifically, recurrence
quantification analysis---to this research area. While a number of excellent
guides can provide detailed explanations of the methods and their statistical
underpinnings [e.g., @riley2005tutorials; @webber1994dynamical;
@webber2005recurrence], one of the most important considerations that should be
briefly summarized here is about data.

@@

## Conclusion
Considering the pervasiveness of social media, it is unsurprising that social
activists and protesters have utilized these platforms to support real-world
mobilization. Here, we quantitatively explored the connection between online
social cohesion and real-world events. In addition to introducing political
scientists to a family of powerful nonlinear dynamics analyses, our results have
serious implications for monitoring global movements in consistent across other
social uprisings. While state-run media in regions of authoritarian rule are
often biased and serve as propaganda for the leader and central government, the
self-organized nature of Twitter provides a new avenue to gain insight into
truths about uprisings and social mobilization. By conceptualizing Twitter and
real-world events as two elements of an inextricably linked dynamical system,
the levels of social cohesion within social media platforms could be monitored
for fluctuations indicating shifts in power and peace. Social media mobilization
may thus help alert the world to citizens' actions and reactions that are
suppressed by government regimes, providing insight into events that may not
otherwise be broadcast and allowing for faster intervention.

>>>>

Finally, the coupling between negative-only event counts and social cohesion
also remained relatively similar but demonstrated some important differences.
First, we see a greater number of windows at above-chance levels for RR,
including an interesting spike around window 32 that suggests a negative
externally focused action taken by Syria prompted a sharp rise in social
cohesion. (This would not have been captured by the target-only dataset.)
Second---like with the all-event data---we see different structuring of the data
through differences in the patterns of DET; above-chance DET only occurrs within
the middle of the observation period, around a time of increased strife (as
noted above).

@@

Nonlinear methods have been transformative for a variety of research areas
[including psychology, @coco2014cross]. One of the goals of the present work was
to introduce variants of one kind of nonlinear method---specifically, recurrence
quantification analysis---to this research area. While a number of excellent
guides can provide detailed explanations of the methods and their statistical
underpinnings [e.g., @riley2005tutorials; @webber1994dynamical;
@webber2005recurrence], one of the most important considerations that should be
briefly summarized here is about data.

@@

## Conclusion
Considering the pervasiveness of social media, it is unsurprising that social
activists and protesters have utilized these platforms to support real-world
mobilization. Here, we quantitatively explored the connection between online
social cohesion and real-world events. In addition to introducing political
scientists to a family of powerful nonlinear dynamics analyses, our results have
serious implications for monitoring global movements across other social
uprisings. While state-run media in regions of authoritarian rule are often
biased and serve as propaganda for the leader and central government, the
self-organized nature of Twitter provides a new avenue to gain insight into
truths about uprisings and social mobilization. By conceptualizing Twitter and
real-world events as two elements of an inextricably linked dynamical system,
the levels of social cohesion within social media platforms could be monitored
for fluctuations indicating shifts in power and peace. Social media mobilization
may thus help alert the world to citizens' actions and reactions that are
suppressed by government regimes, providing insight into events that may not
otherwise be broadcast and allowing for faster intervention.
